Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal

### 2020-11-12 Papers/02_Sound_Representation/SoundRepresentation.tex
minor changes
progress with the paper

\documentclass{article}
\usepackage{lmodern} % Latin Modern Font
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
% \graphicspath{{images/}}
\usepackage[backend=biber]{biblatex}
\usepackage{amsmath}
\usepackage[makeroom]{cancel}

% \usepackage{auto-pst-pdf}

@@

\begin{abstract}

@@

\section{Introduction}

We aim to exploit redundancies in the constitution of a discrete sound wave to formulate an alternative, more compact and thus easier to analyse, representation. Implicit in this affirmation is the somewhat loose assumption that the wave considered is reasonably well behaved, in the sense that redundancies exist to be identified. In contrast with \textcite{2019TarjanoNeuro}, we don't require the signal to be strictly harmonic.

We aim in providing a method that, with minimal manual interference, is able to reduce a digital wave to a more compact and meaningful representation.

@@

\subsection{Pseudo Cycles}

This work proposes the pseudo cycle as the building block of a discrete wave, assuming its parametric shape to be constant throughout the space of the digital signal; in order words, the adjective pseudo is used because the two other descriptions of the wave, namely, the envelope and the length of the pseudo cycles act into the pseudo cycles shape itself, modifying it in function of the time.

@@

Using the envelope detection algorithm presented in \textcite{2020TarjanoRobust} one can identify the frontiers, both positive and negative, of a digital signal: Those are, ideally, respectively composed of the maxima and minima of each pseudo-cycle of a discrete signal.

If we disconsider inaccuracies we could use either one of the frontiers to infer the exact position, wavelength and amplitude of each pseudo-cycle and to, provided that the shape of the wave is also known, reconstruct the original wave with those pieces of information. Consider, for example, the digital signal presented in figure \ref{fig:signalenvelope}
and the extracted frontiers; the signal is an example of the voice of an alto singer, with its frontiers in black.

@@

It can be seen that both frontiers provide approximately the same information about the location of each pseudo-cycle, albeit with a phase difference between them. As the original algorithm proposed in \textcite{2020TarjanoRobust} is meant for envelope detection, maxima or minima that lies close to the already established frontiers are sometimes neglected, without significant impact in the envelope extracted.

This can be seen in the discrete representation of the sound of the key 33 of a grand piano in figure \ref{fig:frontiergaps}, as the black squares and diamonds: intuitively, one can see that some local maxima and minima are missing, compromising the identification of all pseudo cycles. For our purposes, however, it is beneficial to accurately identify as many local maxima and minima, and hence pseudo cycles, as possible, as the impact on the shape of a pseudo cycle is significant.

We are going to assume that all the local extremes identified by the envelope detection algorithm are indeed correct; albeit not being strictily accurate, this approximation is very reasonable and simplifies further steps immensely, as we now need only to idenfity pseudo cycles with periods $ T $, that is, the difference between two adjacent maxima or minima, that are significantly bigger than the average observed in the discrete wave, and identify their local maximum or minimum, respectively.

The result of this procedure can be seen ad the gray squares and diamonds in figure \ref{fig:frontiergaps}.

\begin{figure}[ht!]
  \centering
     \includegraphics{images/02frontiergaps.pdf}
  \caption{Close-up view of a discrete signal representing the sound of the key 33 of a grand piano and its original positive and negative frontiers, in black, as well as the additional extrema identified during the refining process.}
  \label{fig:frontiergaps}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
     \includegraphics{02pcsraw-alto.pdf}
  \caption{Raw pseudo-cycles superimposed as defined by the positive and negative frontiers, for the alto singer signal.}
  \label{fig:pcrawalto}
\end{figure}

We can normalize the amplitude the pseudo-cycles between zero and one, by dividing each of them by their maximum. The lengths of each pseudo-cycle can be normalized with the use of the Fourier transform; to avoid any loss of data, we can use the maximum wavelength as the standard.

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{03pcs-alto.pdf}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Normalized pseudo-cycles superimposed as defined by the positive and negative frontiers, for an alto singer signal, and the average of all normalized pseudo-cycles.}
  \label{fig:pcalto}
\end{figure}

Comparing figures \ref{fig:pcrawalto} and \ref{fig:pcalto} we note the effect of the normalization, as a means to reduce the variance of the pseudo-cycles, specially in the regions near the discontinuities. This will enable a more accurate approximation of the average wave.

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{04averagepc-alto.pdf}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Average pseudo-cycles, superimposed, after a change of phase of $-\pi$ on the average pseudo-cycle defined by the negative frontier, for an alto singer digital signal.}
  \label{fig:averagepc-alto}
\end{figure}

Figure \ref{fig:averagepc-alto} makes clear that the average pseudo-cycles for the alto singer signal, as estimated by both frontiers, are in reasonable agreement, despite the evident vertical asymmetries of the underlying wave.

That is not always the case, however, as figure \ref{fig:averagepc-piano33} illustrates. For a discrete signal representing the recording o the key 33 of a grand piano, we can see that the average pseudo-cycle inferred from the positive frontier is substantially different from the one obtained with the negative frontier.

The horizontal lines indicate the maximum of each pseudo cycle, being the point of adjacency between two subsequent pseudo cycles. For the average defined by the negative frontier we see that there is a local maxima near that middle that is almost as high as the global maxima, which is not the case as the average defined by the positive one.

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{04averagepc-piano33.pdf}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Average pseudo-cycles, superimposed, after a change of phase of $-\pi$ on the average pseudo-cycle defined by the negative frontier, for a grand piano digital signal. The horizontal lines in the figure mark the points of maximum of each of the average pseudo cycles.}
  \label{fig:averagepc-piano33}
\end{figure}

We could take the average of those two representations, but that would dilute the parametric representation of the pseudo-cycle, besides introducing unnecessary complication in the stage of recreating the wave, as we would have to deal with redundant information about the location of each pseudo-cycle.

Instead, a measure of the statistical variance of the lengths of the pseudo cycles will be used in order to select the most appropriate frontier as guide for the construction of the average pseudo cycle waveform.

Figure \ref{fig:std-piano33} shows the distribution of the lengths of the pseudo cycles of the grand piano digital signal. We can use the standard deviation as this measure, and use the pseudo cycles as defined by the frontier with the least standard deviation.

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{05std-piano33.pdf}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Histogram of the distribution of lengths of the pseudo cycles, as defined by the positive and negative frontiers, and the accompanying standard deviation, for a digital signal of the key 33 of a grand piano.}
  \label{fig:std-piano33}
\end{figure}

Thus, a tillable parametric representation of the average pseudo-cycle can be obtained via the least mean squares method; we are interested in the polynomial that best approximates the average pseudo cycle, respecting the conditions that the beginning and the end of this polynomial must coincide, as must the first derivative of that polynomial in those places, if we are to obtain a smooth transition between pseudo cycles.

From \textcite{2013SelesnickLeast} we know that a constrained least mean squares problem of the form $ \underset{A}{\min} ||Q A - Y||^2_2 \quad \text{subject to} \quad V A = B $ has a closed form approximate solution $ \hat{A} = \left(Q^{T} Q\right)^{-1} \left(Q^{T} Y - V^{T} \left(V \left(Q^{T} Q\right)^{-1} V^{T}\right)^{-1} V \left(Q^{T} Q\right)^{-1} Q^{T} Y - B \right) $, where $ Y $ is the vector we are interested in approximating.

We can proceed to define the real vector $ U = \{ u_0, u_1, \cdots, u_{m-1}\} $ as the average of all normalized pseudo-cycles, with $ m \in \mathbb{N} $ equal to the number of elements and the maximum length of the pseudo-cycles identified by the envelope detection algorithm.

As we are interested in maintaining $ C^0 $ and $ C^1 $ continuity between two adjacent pseudo-pulses, it is convenient to define the vector $ Y $ as two vectors $ E $ stacked, that is $ Y = \{ u_0, u_1, \cdots, u_{m-1}, u_0, u_1, \cdots, u_{m-1}\} $.

$ A $, the vector of coefficients we are interested in estimating, will thus be composed of $ 2 (k + 1) $ items, where $ k $ is the order of the polynomial to be used in the approximation. Half those values are redundant, however, and $ A $ can thus be defined as $ A = \{ a_0, a_1, \cdots, a_k, a_0, a_1, \cdots, a_k \} $. $ Q $ is formed as usual, with the difference that
it is duplicated horizontally, as seen in equation \ref{eq:matrix}.

Anticipating that we will eventually evaluate this polynomial in various lengths, it is convenient to normalize $ X $ between $ 0 $ and $ 1 $, defining $ X = \left\{ \cancelto{0}{\frac{0}{m-1}}, \frac{1}{m-1}, \frac{2}{m-1}, \cdots, \cancelto{1}{\frac{m-1}{m-1}} \right\} $

\begin{equation} \label{eq:matrix}
\stackrel{Q_{m \times 2 (k + 1)}} {
\begin{bmatrix}
  1      & x_0     & \cdots & x_0^k   & 1      & x_0     & \cdots & x_0^k   \\
  1      & x_1     & \cdots & x_1^k   & 1      & x_1     & \cdots & x_1^k   \\
  \vdots & \vdots  & \ddots & \vdots  & \vdots & \vdots  & \ddots & \vdots  \\
  1      & x_{m-1} & \cdots & x_{m-1} & 1      & x_{m-1} & \cdots & x_{m-1} \\
\end{bmatrix}
}
\stackrel{A_{2 (k + 1) \times 1}}
{
\begin{bmatrix}
a_0    \\
a_1    \\
\vdots \\
a_k    \\
a_0    \\
a_1    \\
\vdots \\
a_k    \\
\end{bmatrix}
}
=
\stackrel{Y_{2 m \times 1}}
{
\begin{bmatrix}
y_0     \\
y_1     \\
\vdots  \\
y_{m-1} \\
y_0     \\
y_1     \\
\vdots  \\
y_{m-1} \\
\end{bmatrix}
}
\end{equation}

To maintain the continuity and smoothness, as well as the identity between the first and second half of the coefficients, $ V $ can be defined as in equation \ref{eq:constraint}.

\begin{equation} \label{eq:constraint}
\stackrel{V_{k + 3 \times 2 (k + 1)}} {
\begin{bmatrix}
  1      & 0       & \cdots & 0           & -1     & 0        & \cdots & 0                \\
  0      & 1       & \cdots & 0           & 0      & -1       & \cdots & 0                \\
  \vdots & \vdots  & \ddots & \vdots      & \vdots & \vdots   & \ddots & \vdots           \\
  0      & 0       & \cdots & 1           & 0      & 0        & \cdots & -1               \\
  1      & x_0     & \cdots & x_0^k       & -1     & -x_{m-1} & \cdots & -x_{m-1}^k       \\
  0      & 1       & \cdots & k x_0^{k-1} & 0      & -1       & \cdots & -k x_{m-1}^{k-1} \\
\end{bmatrix}
}
\stackrel{A_{2 (k + 1) \times 1}}
{
\begin{bmatrix}
a_0    \\
a_1    \\
\vdots \\
a_k    \\
a_0    \\
a_1    \\
\vdots \\
a_k    \\
\end{bmatrix}
}
=
\stackrel{B_{k + 2 \times 1}}
{
\begin{bmatrix}
0      \\
\vdots \\
0      \\
\end{bmatrix}
}
\end{equation}

The initial $k+1$ lines of $V$ assure that the first half of the coefficients of $A$ are equal to the second half, while the penultimate line ensures $C^0$ continuity and the last line ensures $C^1$ continuity, guaranteeing that the derivatives at the beginning and the end of the parametric pseudo cycles are equal.

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{06approximation-alto}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Two adjacent pseudo-cycles. The detail view illustrates that $C^0$ and $C^1$ smoothness are maintained in the parametric representation when two reconstructions are stacked horizontally.}
  \label{fig:05approximation-alto}
\end{figure}

>>>>

\documentclass{article}
\usepackage{lmodern} % Latin Modern Font
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
% \graphicspath{{images/}}
\usepackage[backend=biber]{biblatex}
\usepackage{amsmath}
\usepackage[makeroom]{cancel}
% \usepackage{auto-pst-pdf}

@@

\begin{abstract}
We propose representing a discrete wave based on the description of the pseudo cycle as a function of time.

@@

\section{Introduction} % 500 words
% Opener sentence -> Question | Assertion | Intriguing Revelations
The idea, based on the Fourier transform theory, that a complex wave can be represented by a sum of sinusoids is ubiquituous in sound processing, owing considerably to the reversebility of the fourier transform.

Despite its many uses, for discrete real waves, frequency and time domain representations are equivalent, as the later represents the discrete with the same number of floats.

Additionally, eventual variations in the envelope of the wave have to be encoded as additional sinusoids \textcite{2019TarjanoNeuro}.

% Literature review | Brief Context of Prior Research
For these reasons, mixed representations were introduced, specially in the context of lossy and lossless sound compression

% Restate Your Question as Something Not Fully Understood by Prior Research -> identify the gap in the literature use but, however, etc…

However, those representations lack a more physical connection, and generally dont lend themselves well as basis representatios for further tasks, such as machine learning synthesis.

% State the Significance of Your Question -> make readers understand why they should read your report
The aim of this work is, then, to fill this gap, introducing a compact representation

% What I did - State Your Claim | Objective | Hypothesis -> should clearly relate to the information gap
We aim to exploit redundancies in the constitution of a discrete sound wave to formulate an alternative, more compact and thus easier to analyse, representation. Implicit in this affirmation is the somewhat loose assumption that the wave considered is reasonably well behaved, in the sense that redundancies exist to be identified.

To that end, we use the cycle as the basic building block of a signal and describe its changes both in the vertical axis, assumed to be due to the varying amplitude of the signal, and in the local horizontal axis, reflecting global frequency variations.

We aim in providing a method that, with minimal manual interference, is able to reduce a digital wave to a more compact and meaningful representation.
% brief outlook on the structure of the paper

@@

\subsection{Identifying the Pseudo Cycles}

This work proposes the (pseudo) cycle as the building block of a discrete wave, assuming its waveform to be constant throughout the space of the digital signal; in other words, the adjective pseudo is used because the two other descriptions of the wave, namely, the envelope and the length of the pseudo cycles act into the pseudo cycles shape itself, modifying it in function of the time, during the lifetime of the signal.

@@

Using the envelope detection algorithm presented in \textcite{2020TarjanoRobust} one can identify the frontiers, both positive and negative, of a digital signal: Those are respectively composed of the maxima and minima of each pseudo-cycle of a discrete signal.

If we disconsider inaccuracies we could use either one of the frontiers indifferently to infer the exact position, waveform and amplitude of each pseudo-cycle and to reconstruct the original wave with those information. Consider, for example, the digital signal presented in figure \ref{fig:signalenvelope}
and the extracted frontiers; the signal is an example of the voice of an alto singer, with its frontiers in black.

@@

It can be seen that both frontiers provide approximately the same information about the location of each pseudo-cycle, albeit with a phase difference between them.

However, as the algorithm proposed in \textcite{2020TarjanoRobust} is originally meant for envelope detection, maxima or minima that lies close to the already established frontiers are sometimes neglected, without significant impact in the shape of the envelope extracted.

This can be seen in the discrete representation of the sound of the key 33 of a grand piano in figure \ref{fig:frontiergaps}, as the black squares and diamonds: intuitively, one can see that some local maxima and minima were not detected, compromising the identification of all pseudo cycles.

For our purposes, however, it is beneficial to accurately identify as many local maxima and minima, and the resulting pseudo cycles, as possible, as the impact on the shape of a pseudo cycle is significant.

We are going to assume that all the local extremes identified by the envelope detection algorithm are indeed correct; albeit not being strictily accurate, this approximation is very reasonable and simplifies further steps immensely, as we now need only to idenfity pseudo cycles with periods $ T $, that is, the difference between two adjacent maxima or minima, that are significantly bigger than the majority of the ones observed in the discrete wave, and identify their local maximum or minimum, respectively.

To that end we are going to use the mode of the periods as the centrality measure, instead of the average. Similarly, we will use the mean absolute deviation in relation to the mode as a measure of the dispersion of the periods.

In figure \ref{fig:modevsaverage} an except of the plot of the frequency of the errors is shown for both measures, for the case of a discrete wave representing the sound of the key 33 of a grand piano.

The errors are the frequency of absolute difference between the centrality of the distribution of all combined periods, as defined by both the positive and negative frontiers, and their values.

In addition to the smaller mean absolute deviation, the errors when the mode is used are centered around zero, which is not the case for when the centrality measure used is the average.

\begin{figure}[ht!]
  \centering
     \includegraphics{images/02modevsaverage.pdf}
  \caption{Frequency of errors for the periods of a digital signal representing the sound of the key 33 of a grand piano when two different centrality measures are used: the mode of the periods and their average.}
  \label{fig:modevsaverage}
\end{figure}

The result of this procedure can be seen as the additional squares and diamonds in figure \ref{fig:frontiergaps}, representing new maxima and minima, respectively, found by reanalising pulses whose period is superior to 2 mean absolute deviations from the mode of the periods distribution, both for the positive and the negative frontiers.

A new mode is then calculated from the new pulse distribution, as well as the mean absolute deviation; the procedure is repeated until no more new pseudo pulses are found or the mean absolute deviation is increased by the addition of the newfound extrema.

\begin{figure}[ht!]
  \centering
     \includegraphics{images/03frontiergaps.pdf}
  \caption{Close-up view of a discrete signal representing the sound of the key 33 of a grand piano and its original positive and negative frontiers, in black, as well as the additional extrema identified during the refining process.}
  \label{fig:frontiergaps}
\end{figure}

figure \ref{fig:plotXps} illustrates the behaviour of the periods as inferred by both frontiers, before and after the refinement.

\begin{figure}[ht!]
  \centering
     \includegraphics{images/04plotXps.pdf}
  \caption{Frame of occurrence of the maxima and minima of a discrete signal representing the sound of the key 33 of a grand piano before and after the refinement process.}
  \label{fig:plotXps}
\end{figure}

\subsection{Pseudo Cycles evolution over time}

@@

% \begin{figure}[ht!]
%   \centering
%      \includegraphics{02pcsraw-alto.pdf}
%   \caption{Raw pseudo-cycles superimposed as defined by the positive and negative frontiers, for the alto singer signal.}
%   \label{fig:pcrawalto}
% \end{figure}

% We can normalize the amplitude the pseudo-cycles between zero and one, by dividing each of them by their maximum. The lengths of each pseudo-cycle can be normalized with the use of the Fourier transform; to avoid any loss of data, we can use the maximum wavelength as the standard.

% \begin{figure}[ht!]
%   \centering
%     %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
%      \includegraphics{03pcs-alto.pdf}
%     % \def\svgwidth{\linewidth}
%     %\input{01signalenvelope.pdf_tex}
%   \caption{Normalized pseudo-cycles superimposed as defined by the positive and negative frontiers, for an alto singer signal, and the average of all normalized pseudo-cycles.}
%   \label{fig:pcalto}
% \end{figure}

% Comparing figures \ref{fig:pcrawalto} and \ref{fig:pcalto} we note the effect of the normalization, as a means to reduce the variance of the pseudo-cycles, specially in the regions near the discontinuities. This will enable a more accurate approximation of the average wave.

% \begin{figure}[ht!]
%   \centering
%     %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
%      \includegraphics{04averagepc-alto.pdf}
%     % \def\svgwidth{\linewidth}
%     %\input{01signalenvelope.pdf_tex}
%   \caption{Average pseudo-cycles, superimposed, after a change of phase of $-\pi$ on the average pseudo-cycle defined by the negative frontier, for an alto singer digital signal.}
%   \label{fig:averagepc-alto}
% \end{figure}

% Figure \ref{fig:averagepc-alto} makes clear that the average pseudo-cycles for the alto singer signal, as estimated by both frontiers, are in reasonable agreement, despite the evident vertical asymmetries of the underlying wave.

% That is not always the case, however, as figure \ref{fig:averagepc-piano33} illustrates. For a discrete signal representing the recording o the key 33 of a grand piano, we can see that the average pseudo-cycle inferred from the positive frontier is substantially different from the one obtained with the negative frontier.

% The horizontal lines indicate the maximum of each pseudo cycle, being the point of adjacency between two subsequent pseudo cycles. For the average defined by the negative frontier we see that there is a local maxima near that middle that is almost as high as the global maxima, which is not the case as the average defined by the positive one.

% \begin{figure}[ht!]
%   \centering
%     %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
%      \includegraphics{04averagepc-piano33.pdf}
%     % \def\svgwidth{\linewidth}
%     %\input{01signalenvelope.pdf_tex}
%   \caption{Average pseudo-cycles, superimposed, after a change of phase of $-\pi$ on the average pseudo-cycle defined by the negative frontier, for a grand piano digital signal. The horizontal lines in the figure mark the points of maximum of each of the average pseudo cycles.}
%   \label{fig:averagepc-piano33}
% \end{figure}

% We could take the average of those two representations, but that would dilute the parametric representation of the pseudo-cycle, besides introducing unnecessary complication in the stage of recreating the wave, as we would have to deal with redundant information about the location of each pseudo-cycle.

% Instead, a measure of the statistical variance of the lengths of the pseudo cycles will be used in order to select the most appropriate frontier as guide for the construction of the average pseudo cycle waveform.

% Figure \ref{fig:std-piano33} shows the distribution of the lengths of the pseudo cycles of the grand piano digital signal. We can use the standard deviation as this measure, and use the pseudo cycles as defined by the frontier with the least standard deviation.

% \begin{figure}[ht!]
%   \centering
%     %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
%      \includegraphics{05std-piano33.pdf}
%     % \def\svgwidth{\linewidth}
%     %\input{01signalenvelope.pdf_tex}
%   \caption{Histogram of the distribution of lengths of the pseudo cycles, as defined by the positive and negative frontiers, and the accompanying standard deviation, for a digital signal of the key 33 of a grand piano.}
%   \label{fig:std-piano33}
% \end{figure}

% Thus, a tillable parametric representation of the average pseudo-cycle can be obtained via the least mean squares method; we are interested in the polynomial that best approximates the average pseudo cycle, respecting the conditions that the beginning and the end of this polynomial must coincide, as must the first derivative of that polynomial in those places, if we are to obtain a smooth transition between pseudo cycles.

% From \textcite{2013SelesnickLeast} we know that a constrained least mean squares problem of the form $ \underset{A}{\min} ||Q A - Y||^2_2 \quad \text{subject to} \quad V A = B $ has a closed form approximate solution $ \hat{A} = \left(Q^{T} Q\right)^{-1} \left(Q^{T} Y - V^{T} \left(V \left(Q^{T} Q\right)^{-1} V^{T}\right)^{-1} V \left(Q^{T} Q\right)^{-1} Q^{T} Y - B \right) $, where $ Y $ is the vector we are interested in approximating.

% We can proceed to define the real vector $ U = \{ u_0, u_1, \cdots, u_{m-1}\} $ as the average of all normalized pseudo-cycles, with $ m \in \mathbb{N} $ equal to the number of elements and the maximum length of the pseudo-cycles identified by the envelope detection algorithm.

% As we are interested in maintaining $ C^0 $ and $ C^1 $ continuity between two adjacent pseudo-pulses, it is convenient to define the vector $ Y $ as two vectors $ E $ stacked, that is $ Y = \{ u_0, u_1, \cdots, u_{m-1}, u_0, u_1, \cdots, u_{m-1}\} $.

% $ A $, the vector of coefficients we are interested in estimating, will thus be composed of $ 2 (k + 1) $ items, where $ k $ is the order of the polynomial to be used in the approximation. Half those values are redundant, however, and $ A $ can thus be defined as $ A = \{ a_0, a_1, \cdots, a_k, a_0, a_1, \cdots, a_k \} $. $ Q $ is formed as usual, with the difference that
% it is duplicated horizontally, as seen in equation \ref{eq:matrix}.

% Anticipating that we will eventually evaluate this polynomial in various lengths, it is convenient to normalize $ X $ between $ 0 $ and $ 1 $, defining $ X = \left\{ \cancelto{0}{\frac{0}{m-1}}, \frac{1}{m-1}, \frac{2}{m-1}, \cdots, \cancelto{1}{\frac{m-1}{m-1}} \right\} $

% \begin{equation} \label{eq:matrix}
% \stackrel{Q_{m \times 2 (k + 1)}} {
% \begin{bmatrix}
%   1      & x_0     & \cdots & x_0^k   & 1      & x_0     & \cdots & x_0^k   \\
%   1      & x_1     & \cdots & x_1^k   & 1      & x_1     & \cdots & x_1^k   \\
%   \vdots & \vdots  & \ddots & \vdots  & \vdots & \vdots  & \ddots & \vdots  \\
%   1      & x_{m-1} & \cdots & x_{m-1} & 1      & x_{m-1} & \cdots & x_{m-1} \\
% \end{bmatrix}
% }
% \stackrel{A_{2 (k + 1) \times 1}}
% {
% \begin{bmatrix}
% a_0    \\
% a_1    \\
% \vdots \\
% a_k    \\
% a_0    \\
% a_1    \\
% \vdots \\
% a_k    \\
% \end{bmatrix}
% }
% =
% \stackrel{Y_{2 m \times 1}}
% {
% \begin{bmatrix}
% y_0     \\
% y_1     \\
% \vdots  \\
% y_{m-1} \\
% y_0     \\
% y_1     \\
% \vdots  \\
% y_{m-1} \\
% \end{bmatrix}
% }
% \end{equation}

% To maintain the continuity and smoothness, as well as the identity between the first and second half of the coefficients, $ V $ can be defined as in equation \ref{eq:constraint}.

% \begin{equation} \label{eq:constraint}
% \stackrel{V_{k + 3 \times 2 (k + 1)}} {
% \begin{bmatrix}
%   1      & 0       & \cdots & 0           & -1     & 0        & \cdots & 0                \\
%   0      & 1       & \cdots & 0           & 0      & -1       & \cdots & 0                \\
%   \vdots & \vdots  & \ddots & \vdots      & \vdots & \vdots   & \ddots & \vdots           \\
%   0      & 0       & \cdots & 1           & 0      & 0        & \cdots & -1               \\
%   1      & x_0     & \cdots & x_0^k       & -1     & -x_{m-1} & \cdots & -x_{m-1}^k       \\
%   0      & 1       & \cdots & k x_0^{k-1} & 0      & -1       & \cdots & -k x_{m-1}^{k-1} \\
% \end{bmatrix}
% }
% \stackrel{A_{2 (k + 1) \times 1}}
% {
% \begin{bmatrix}
% a_0    \\
% a_1    \\
% \vdots \\
% a_k    \\
% a_0    \\
% a_1    \\
% \vdots \\
% a_k    \\
% \end{bmatrix}
% }
% =
% \stackrel{B_{k + 2 \times 1}}
% {
% \begin{bmatrix}
% 0      \\
% \vdots \\
% 0      \\
% \end{bmatrix}
% }
% \end{equation}

% The initial $k+1$ lines of $V$ assure that the first half of the coefficients of $A$ are equal to the second half, while the penultimate line ensures $C^0$ continuity and the last line ensures $C^1$ continuity, guaranteeing that the derivatives at the beginning and the end of the parametric pseudo cycles are equal.

% \begin{figure}[ht!]
%   \centering
%     %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
%      \includegraphics{06approximation-alto}
%     % \def\svgwidth{\linewidth}
%     %\input{01signalenvelope.pdf_tex}
%   \caption{Two adjacent pseudo-cycles. The detail view illustrates that $C^0$ and $C^1$ smoothness are maintained in the parametric representation when two reconstructions are stacked horizontally.}
%   \label{fig:05approximation-alto}
% \end{figure}
